---
title: "PeerAssessment1"
output:
  html_document: default
  keep_md: true
#  md_document:
#           variant: markdown_github
---



## Loading and preprocessing the data
```{r loarding}
unzip("repdata_data_activity.zip")
raw_data <- read.csv("activity.csv")
raw_data$date <- as.Date(raw_data$date)

library(dplyr)
library(knitr)
library(ggplot2)

```


## What is mean total number of steps taken per day?

```{r TotalNumberPerDay}

steps_per_day <- raw_data %>% 
                select("steps","date") %>% 
                group_by(date) %>% 
                summarise_at("steps",sum,na.rm = T)
ggplot(steps_per_day, aes(x = steps)) + geom_histogram(fill = "blue",binwidth = 1000) + labs(title = "Histogram of Steps per Day") 

```



## What is the average daily activity pattern?

```{r Interval}

Steps_per_Interval <- raw_data %>%
        group_by(interval) %>%
        summarise_at("steps", mean, na.rm = T)

ggplot(Steps_per_Interval ,aes(x = interval, y = steps)) + geom_line(color = "green")+labs(title = "Average Daily Activity Pattern") 

max <- round(Steps_per_Interval [which.max(Steps_per_Interval$steps),],0)

kable(max,caption = "Maxiumum Steps and Interval",)

```



## Imputing missing values

- Total Number of Missing Value

```{r}
missing_val <- sum(is.na(raw_data$steps))
missing_val_percent <- round(mean(is.na(raw_data$steps)) * 100,0)
```

The total number of missing values are `r missing_val`, `r missing_val_percent`%

- Fill in all of the missing value in the dataset

```{r}
Interval_mean <- mean(Steps_per_Interval$steps,na.rm = T)

fill_data <- raw_data

fill_data$steps[is.na(fill_data$steps)] <- Interval_mean

sum(is.na(fill_data$steps))

```

- Make a histogram of total number of steps each day, report the mean and median.
```{r}
steps_per_day2 <- fill_data %>%  
                select("steps","date") %>% 
                group_by(date) %>% 
                summarise_at("steps",sum,na.rm = T)

ggplot(steps_per_day2,aes(x = steps)) + geom_histogram(fill = "red",binwidth = 1000) + labs(title = "Histogram of Steps per Day(Imputing Missing Value)") 
```

```{r}
new_mean <-round(mean(steps_per_day2$steps),3)
new_median <- round(median(steps_per_day2$steps),3)
```

New Mean is `r new_mean`, New Median is `r new_median`

## Are there differences in activity patterns between weekdays and weekends?

```{r}
fill_data$weekday <- as.factor(weekdays(fill_data$date))

weekend_data <- fill_data %>% filter(weekday == "土曜日"|weekday == "日曜日")
weekday_data <- fill_data %>% filter(weekday != "土曜日"& weekday != "日曜日")

weekend_data[,"weekend"] <- "weekend" 
weekday_data[,"weekend"] <- "weekday" 

bind_data <- rbind(weekend_data,weekday_data)
bind_data$weekend <- as.factor(bind_data$weekend)

week_data <- bind_data %>% group_by(weekend,interval) %>% summarise_at("steps",mean)

```

```{r}
ggplot(week_data,aes(x = interval, y = steps)) + geom_line(color = "orange") + facet_wrap(~ weekend, nrow = 2) + labs(x = "Interval", y = "Numbers of steps")

```
